\subsection{Multi-label classification using Learning Classifier Systems}

\noindent Context: Diploma Thesis
\noindent Aristotle University of Thessaloniki, Thessaloniki, Greece; 2013

\noindent \href{https://github.com/li9i/lcss}{\texttt{[Code]}}

\begin{problem}
Assume a set of annotated data of multiple labels (not
multiple classes: each instance is simultaneously classified to more than one
labels). Given this set, we would like to build a classifier which, trained with
this set, can classify unseen data to multiple labels with the highest accuracy
possible.
\end{problem}

The solution was sought after through extending the framework of Learning
Classifier Systems to the multi-label dimension. LCS's are systems that
represent data instances with rules of the form ``antecedents $\Rightarrow$
consequents". Within this frame, rules are treated as a population evolving
through time according to the principles of evolution mapped out by Charles
Darwin. Rules undergo (a) crossover with other rules depending on a measure of
their fitness (their ``quality"), and (b) mutations indiscriminately during
crossover, through time, iteratively.

The resulting classifier, called GMl-ASLCS, was compared against the
state-of-the-art classifiers on a number of datasets and its performance was
found to be (a) overall the highest in terms of accuracy, and (b) not
statistically significantly divergent than those it was compared against. Table
\ref{table:accuracyBasedComparison} shows the accuracy of the designed LCS
called GMl-ASLCS and that of its rivals on 6 standard multi-label datasets.

\begin{table}[!h]
  \begin{center}
    \begin{tabular}{l|cccccc|c}
    Algorithms / Datasets& music     & yeast     & genbase       & scene     & medical   & enron     & Rank \\
    \toprule \\ [-2ex]
    GMl-ASLCS         & $\textbf{60.47}^1$ & $\textbf{51.67}^1$ & $\textbf{98.63}^1$  & $63.15^2$ & $51.58^3$ & $40.35^2$ & $\textbf{1.67}^1$ \\
    GMl-ASLCS$_{\:0}$ & $50.05^4$ & $45.51^4$ & $87.90^5$     & $42.39^5$ & $40.14^5$ & $39.40^3$ & $4.33^5$                                  \\
    BR-J48            & $46.23^5$ & $43.95^5$ & $98.62^{2.5}$ & $51.34^4$ & $\textbf{74.26}^1$ & $36.71^4$ & $3.58^4$                         \\
    RA$k$EL-J48       & $50.91^3$ & $48.74^3$ & $98.62^{2.5}$ & $57.76^3$ & $72.84^2$ & $\textbf{41.04}^1$ & $2.42^2$                         \\
    Ml$k$NN           & $53.26^2$ & $51.62^2$ & $94.11^4$     & $\textbf{66.14}^1$ & $41.77^4$ & $31.84^5$ & $3.00^3$                         \\ \bottomrule
    \end{tabular}
    \caption{\small Comparison between GMl-ASLCS and rival multi-label
             classifier algorigthms.  The exponents refer to the rank of each
             algorithm on each specific dataset.  Column ``Rank" summarises the
             overall rank of each classifier}
	\label{table:accuracyBasedComparison}
    \end{center}
\end{table}

\begin{itemize}
  \item Notions/resources/tools used: Genetic algorithms, \texttt{Java}, \texttt{git}
\end{itemize}
